---
title: "HHA"
output: flexdashboard::flex_dashboard
runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
library(DT)
library(data.table)
library(corrplot)
library(dplyr)
library(ggplot2)
library(glmnet)
library(mice)
library(purrr)
assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")


opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

```

```{r source_functions}
source("functions.R")
```


```{css}
.datatables.html-widget.html-widget-static-bound{
  height: auto !important;
  width: 90vw !important;
}
.dataTables_scrollBody{
  height: unset !important;
}
```

```{r functions}

top.n.select <- function(id, title){
  selectInput(inputId = id, label = title, choices = c("", 5,10,20))
}

digits.select <- function(id, title){
  selectInput(inputId = id, label = title, choices = c(0,1,2,3), selected = 2)
}

custom.select <- function(id, title, vars, multiple.select = T){
  selectInput(inputId = id,
              label = title,
              choices = vars,
              selected = ifelse(multiple.select == T, vars, vars[1]),
              multiple = multiple.select)
}

percentage.checkbox <- function(id,title){
  checkboxInput(inputId = id, label= title, value = T)
}


get.q1.id = function(id){return (paste0("q1_",id))}

get.q2.id = function(id){return (paste0("q2_",id))}

get.q3.id = function(id){return (paste0("q3_",id))}

get.q4.id = function(id){return (paste0("q4_",id))}

get.q5.id = function(id){return (paste0("q5_",id))}

get.q6.id = function(id){return (paste0("q6_",id))}
```

```{r load_data}
HHA = read.csv("HHA All Providers.csv")
HHA = HHA[!is.na(HHA$Quality.of.Patient.Care.Star.Rating), ]
```

```{r constants}
# how.cols <- colnames(PPR)[18:33]
# Offers.Cols <- colnames(PPR)[9:14]
```

```{r clean_data}
#Create two data frames for further analysis
#HHA_common is a data frame that contains common and numerical variables (excluding PPR-related variables) from 2015 to 2022
HHA_common = HHA[, c(1:4, 6:7, 9:21, 23, 26:27, 29, 31:32)]

#HHA_PPR is a data frame that contains common and numerical variables from 2019 to 2022 particularly for PPR-related analysis
HHA_PPR = HHA[, c(1:4, 6:7, 9:21, 23, 26:27, 29, 31:32, 34, 46:62)]
HHA_PPR = HHA_PPR[HHA_PPR$Year == 2019 | HHA_PPR$Year == 2020 | HHA_PPR$Year == 2021 | HHA_PPR$Year == 2022, ]
HHA_PPR = HHA_PPR[!is.na(HHA_PPR$DTC.Observed.Rate), ]

#Data frames below contain results from respective years for detailed analysis
HHA_15_16 = HHA[HHA$Year == 2015 | HHA$Year == 2016, ][, c(9:33, 35:43)]
HHA_17_18 = HHA[HHA$Year == 2017 | HHA$Year == 2018, ][, c(9:29, 31:33, 35:38)]
HHA_19 = HHA[HHA$Year == 2019, ][, c(9:29, 31:38, 44:45, 47:62)]
HHA_20 = HHA[HHA$Year == 2020, ][, c(9:29, 31:32, 34, 46:62)]
HHA_21_22 = HHA[HHA$Year == 2021 | HHA$Year == 2022, ][, c(9:21, 23, 26:27, 29, 31:32, 34, 46:62)]
```

```{r define_variables}
#Survey items in 2015 and 2016
items_2015 = c("Quality.of.Patient.Care.Star.Rating", "How.often.the.home.health.team.began.their.patients..care.in.a.timely.manner", "How.often.the.home.health.team.taught.patients..or.their.family.caregivers..about.their.drugs", "How.often.the.home.health.team.determined.whether.patients.received.a.flu.shot.for.the.current.flu.season", "How.often.the.home.health.team.checked.patients..risk.of.falling", "How.often.patients.got.better.at.walking.or.moving.around", "How.often.the.home.health.team.checked.patients.for.depression", "How.often.the.home.health.team.made.sure.that.their.patients.have.received.a.pneumococcal.vaccine..pneumonia.shot..", "How.often.patients.got.better.at.getting.in.and.out.of.bed", "How.often.patients.got.better.at.bathing", "With.diabetes..how.often.the.home.health.team.got.doctor.s.orders..gave.foot.care..and.taught.patients.about.foot.care", "How.often.patients.got.better.at.taking.their.drugs.correctly.by.mouth", "How.often.the.home.health.team.checked.patients.for.pain", "How.often.patients.had.less.pain.when.moving.around", "How.often.patients..breathing.improved", "How.often.patients..wounds.improved.or.healed.after.an.operation", "How.often.the.home.health.team.treated.their.patients..pain", "How.often.the.home.health.team.treated.heart.failure..weakening.of.the.heart..patients..symptoms", "How.often.the.home.health.team.took.doctor.ordered.action.to.prevent.pressure.sores..bed.sores.", "How.often.the.home.health.team.included.treatments.to.prevent.pressure.sores..bed.sores..in.the.plan.of.care", "How.often.the.home.health.team.checked.patients.for.the.risk.of.developing.pressure.sores..bed.sores." )

#Survey items in 2021 and 2022
items_2021 = c("Quality.of.Patient.Care.Star.Rating", "How.often.the.home.health.team.began.their.patients..care.in.a.timely.manner", "How.often.the.home.health.team.taught.patients..or.their.family.caregivers..about.their.drugs", "How.often.the.home.health.team.determined.whether.patients.received.a.flu.shot.for.the.current.flu.season", "How.often.patients.got.better.at.walking.or.moving.around", "How.often.patients.got.better.at.getting.in.and.out.of.bed", "How.often.patients.got.better.at.bathing", "How.often.patients.got.better.at.taking.their.drugs.correctly.by.mouth", "How.often.patients.receiving.home.health.care.needed.urgent..unplanned.care.in.the.ER.without.being.admitted", "How.often.home.health.patients.had.to.be.admitted.to.the.hospital", "How.often.physician.recommended.actions.to.address.medication.issues.were.completely.timely", "Changes.in.skin.integrity.post.acute.care..pressure.ulcer.injury", "DTC.Observed.Rate", "DTC.Risk.Standardized.Rate", "PPR.Observed.Rate", "PPR.Risk.Standardized.Rate", "How.much.Medicare.spends.on.an.episode.of.care.at.this.agency..compared.to.Medicare.spending.across.all.agencies.nationally", "No..of.episodes.to.calc.how.much.Medicare.spends.per.episode.of.care.at.agency..compared.to.spending.at.all.agencies..national.")
```


```{r function}
# Initialize a list to store the best Type.of.Ownership for each column based on mean and median
best_performers_mean_2015 = list()
best_performers_median_2015 = list()

# Loop through each column name and find the Type.of.Ownership with the highest mean and median
for (col_name in items_2015) {
  # Calculate mean and median for each Type.of.Ownership
  result_df = HHA_15_16 %>%
    group_by(Type.of.Ownership) %>%
    summarize(mean_value = mean(!!sym(col_name)),
              median_value = median(!!sym(col_name)))
  
  # Find the row with the highest mean_value
  best_mean_row = result_df[which.max(result_df$mean_value), ]
  best_mean_row$Performance_Measure = "Mean"
  best_mean_row$Column_Name = col_name
  
  # Find the row with the highest median_value
  best_median_row = result_df[which.max(result_df$median_value), ]
  best_median_row$Performance_Measure = "Median"
  best_median_row$Column_Name = col_name
  
  # Store the summary tables in the respective lists
  best_performers_mean_2015[[col_name]] = best_mean_row
  best_performers_median_2015[[col_name]] = best_median_row
}

# Initialize a list to store the best Type.of.Ownership for each column based on mean and median
best_performers_mean_2021 = list()
best_performers_median_2021 = list()

# Loop through each column name and find the Type.of.Ownership with the highest mean and median
for (col_name in items_2021) {
  # Calculate mean and median for each Type.of.Ownership
  result_df = HHA_21_22 %>%
    group_by(Type.of.Ownership) %>%
    summarize(mean_value = mean(!!sym(col_name)),
              median_value = median(!!sym(col_name)))
  
  # Find the row with the highest mean_value
  best_mean_row = result_df[which.max(result_df$mean_value), ]
  best_mean_row$Performance_Measure = "Mean"
  best_mean_row$Column_Name = col_name
  
  # Find the row with the highest median_value
  best_median_row = result_df[which.max(result_df$median_value), ]
  best_median_row$Performance_Measure = "Median"
  best_median_row$Column_Name = col_name
  
  # Store the summary tables in the respective lists
  best_performers_mean_2021[[col_name]] = best_mean_row
  best_performers_median_2021[[col_name]] = best_median_row
}

corrplot.output <- function(dat){
  #Generating correlation heat map with common data
  #Identify the numerical columns (excluding the "quality score" column)
  numerical_columns = dat[, sapply(dat, is.numeric)]
  #Exclude the "quality score" column from the numerical columns
  numerical_data = numerical_columns[, !names(numerical_columns) %in% "Quality.of.Patient.Care.Star.Rating"]
  #Calculate the correlation matrix between "quality score" and other numerical variables
  cor_matrix = cor(numerical_data, dat$Quality.of.Patient.Care.Star.Rating, use = "pairwise.complete.obs")
  #Create the correlation heat map
  corrplot(cor_matrix, method = "color", tl.cex = 0.7)
}


correlation.output.PPR <- function(observed.rate) {
  cor_coef = cor(HHA_PPR$Quality.of.Patient.Care.Star.Rating, observed.rate, use = "complete.obs")
  cor_test = cor.test(HHA_PPR$Quality.of.Patient.Care.Star.Rating, observed.rate, method = "pearson")
  return(data.table(`Correlation Coefficient` = cor_coef, `P-Value` = cor_test$p.value))
  
}

correlation.output.common <- function(dat,observed.rate) {
  cor_coef = cor(dat$Quality.of.Patient.Care.Star.Rating, observed.rate, use = "complete.obs")
  cor_test = cor.test(dat$Quality.of.Patient.Care.Star.Rating, observed.rate, method = "pearson")
  return(data.table(`Correlation Coefficient` = cor_coef, `P-Value` = cor_test$p.value))
  
}

anova.output.PPR <- function(input.name){
  the.formula <- as.formula(paste0("Quality.of.Patient.Care.Star.Rating ~ ", input.name ))
  model_dtc = lm(the.formula, data = HHA_PPR)
  return(anova(model_dtc))
}

t.test.output <- function(x){
  y = HHA_common[x == 1, "Quality.of.Patient.Care.Star.Rating" ]
  n = HHA_common[x == 0, "Quality.of.Patient.Care.Star.Rating"]
  if (length(n) == 0){
    return(data.table(`Correlation Coefficent` = 0, p.value = 0))
  }
   if (length(y) == 0){
    return(data.table(`Correlation Coefficent` = 0, p.value = 0))
   }
  t.test.var <- t.test(y,n)
  return(data.table(`Correlation Coefficent`= t.test.var$statistic, p.value = t.test.var$p.value))
}
```




Introduction
=====================================  

We are analyzing data of home health care agencies (HHA) to understand the relationship between their services, ownership types, agency age, and patient care outcomes.

The data that was analyzed contains information on multiple HHAs from 2015 to 2022.

All correlations are based on Quality of Patient Rating

Select the different tabs to proceed with the different analysis and visualizations.


Influential Variables
===================================


Row {data-height=500}
-------------------------------------

```{r q1_input}
inputPanel(
  custom.select(get.q1.id("inputs"),"Choose Inputs:",c("PPR","common"),F)
)
```


```{r q1_output}
renderPlot({
  dat <- HHA_PPR
  if(input$q1_inputs=="common"){
    dat <- HHA_common
  }
  corrplot.output(dat)
})
```

Correlation of PPR/DTC 
=====================================  


Row {data-height=500}
-------------------------------------

```{r q2_input}
inputPanel(
  custom.select(get.q2.id("inputs"), "Choose Inputs:", c("PPR", "DTC"), F)
)
```

Row {data-height=500}
-------------------------------------

```{r q2_output}

HTML("<h3>Correlation</h3><br>")
renderDataTable({
  observed.rate <- HHA_PPR$PPR.Observed.Rate
  if(input$q2_inputs == "DTC"){
    observed.rate <- HHA_PPR$DTC.Observed.Rate
  }
  correlation.output.PPR(observed.rate)
})

HTML("<h3>Performance Categorization</h3><br>")
renderDataTable({
 performance.categorization <- "PPR.Performance.Categorization"
  if(input$q2_inputs == "DTC"){
    performance.categorization <- "DTC.Performance.Categorization"
  }
  anova.output.PPR(performance.categorization)
})

```


Correlation of Service Offerings
=====================================  

Row {data-height=500}
-------------------------------------


```{r q3_input}
service.cols <- HHA_common%>%select(ends_with("Services"))

inputPanel(
  custom.select(get.q3.id("inputs"), "Choose Inputs:", names(service.cols),F)
)
```

Row {data-height=500}
-------------------------------------

```{r q3_output}
renderDataTable({
  t.test.output(HHA_common%>%select(input$q3_inputs))
})
```

Ownership Type
=====================================  

Row {data-height=500}
-------------------------------------

```{r q4_input}
inputPanel(
  sliderInput(inputId = get.q4.id("inputs"), label = "Select Year", min = HHA_common%>%select(Year)%>%min(), max = HHA_common%>%select(Year)%>%max(), value = 2015, step = 1)
)
```


```{r q4_output}
renderPlot({
  year <- input$q4_inputs
  res_trend = HHA_common %>%filter(Year>=year) %>%
  group_by(Type.of.Ownership, Year) %>%
  summarise(Mean = mean(Quality.of.Patient.Care.Star.Rating), Median = median(Quality.of.Patient.Care.Star.Rating), SD = sd(Quality.of.Patient.Care.Star.Rating))
  #res_trend

ggplot(res_trend, aes(x = Year, y = Mean, color = Type.of.Ownership, group = Type.of.Ownership)) +
  geom_line() +
  labs(title = "Mean Quality of Patient Care Star Rating by Ownership Type over Years",
       x = "Year",
       y = "Mean Quality of Patient Care Star Rating",
       color = "Type of Ownership") +
  theme_minimal() +
  ylim(2.75, 3.5)

})

renderPlot({
  year <- input$q4_inputs
  res_trend = HHA_common %>%filter(Year>=year) %>%
  group_by(Type.of.Ownership, Year) %>%
  summarise(Mean = mean(Quality.of.Patient.Care.Star.Rating), Median = median(Quality.of.Patient.Care.Star.Rating), SD = sd(Quality.of.Patient.Care.Star.Rating))
  #res_trend

ggplot(HHA_common%>%filter(Year>=year), aes(x = Type.of.Ownership, y = Quality.of.Patient.Care.Star.Rating)) +
  geom_boxplot() +
  labs(title = "Quality of Patient Care Star Rating by Ownership Type",
       x = "Ownership Type",
       y = "Quality of Patient Care Star Rating",
       fill = "Type of Ownership") +
  theme_minimal()
})
# HHA_common %>%filter(Year>2015) %>%
#   group_by(Type.of.Ownership, Year) %>%
#   summarise(Mean = mean(Quality.of.Patient.Care.Star.Rating), Median = median(Quality.of.Patient.Care.Star.Rating), SD = sd(Quality.of.Patient.Care.Star.Rating))

```

Correlation of Age of HHA
=====================================  

Row {data-height=500}
-------------------------------------


```{r q5_input}
inputPanel(
  sliderInput(inputId = get.q5.id("inputs"), label = "Select Minimum Year Certified", min = HHA_common%>%select(Year.Certified)%>%min(), max = HHA_common%>%select(Year.Certified)%>%max(), value = 2000, step = 1)
)
```


```{r q5_output}

renderDataTable({
  year <- input$q5_inputs
  age.by.certification <- HHA_common%>%filter(Year.Certified>year)%>%select(Age)
  correlation.output.common(HHA_common%>%filter(Year.Certified>year), age.by.certification$Age)
})

```

Correlation Risk of Falling
=====================================  

Row {data-height=500}
-------------------------------------


```{r q6_input}

```


```{r q6_output}
renderDataTable({
  cor_fall_coef = cor(HHA$Quality.of.Patient.Care.Star.Rating, HHA$How.often.the.home.health.team.checked.patients..risk.of.falling, use = "complete.obs")
  cor_fall_test = cor.test(HHA$Quality.of.Patient.Care.Star.Rating, HHA$How.often.the.home.health.team.checked.patients..risk.of.falling, method = "pearson")
  data.table(`Correlation Coefficient` = cor_fall_coef, `P-Value` = cor_fall_test$p.value)
  
})
```